---
output:
  html_document:
    css: www/styles.css
    anchor_sections: FALSE
    includes:
      in_header: "header_manual.html"

params:
  year_curr: 2024 # Current year of sampling
  all_years: TRUE # If FALSE, only reports on year_curr; TRUE reports on all years; Not enabled yet. Currently all years.
  
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '', scipen = 100)
```

```{r imports, include = FALSE}
library(waterNETN)
library(tidyverse)
library(knitr)
library(kableExtra)
library(DT) # for notes datatable
library(htmltools) # for tags with datatable

importData()
year_curr = params$year_curr
year_range = if(params$all_years == TRUE){2006:year_curr} else {year_curr}
```


Water Quality Control checking for NETN `r paste(year_curr, collapse = ", ")` {.tabset .tabset-pills}
---

```{r, include = F, results = 'hide'}
source("QC_NETN_report_functions.R")
source('QC_NETN_report_compile.R')
```

## QC checks {.tabset}
### Summary {.tabset}
The table below documents Quality Control checks performed on NETN water quality and quantity data, along with number of records returned on each check. If any records were returned for a given check, the row is highlighted in the table, and a separate tab corresponding to that check will appear within its associated Data Tab. Yellow indicates a likely error, while blue indicates an anomalous record that requires further review to determine if it's an error or correct. 
```{r}
QC_check_table
```

### Sample Events {.tabset}
```{r eval = comp_include, results = 'asis'}
cat("#### Completedness {.tabset}", "\n\n")
check_null_print(complete_kbl, 5, "Comp Parks")

# Add site-completedness here
```

#### Compiled Notes {.tabset}
```{r}
notes_dt
```

#### Sampling Matrix {.tabset}
```{r}
samp_tab 
```


```{r eval = wqual_include, results = "asis"}
cat("### Water Quality {.tabset}", "\n\n")
```

```{r eval = sonde_include, results = 'asis'}
cat("#### Sonde Parameters {.tabset}", "\n\n")

check_null_print(tbl_DO_mgL_99, 5, "DO 99pct")
check_null_print(tbl_DO_mgL_01, 5, "DO 1pct")

check_null_print(tbl_pH_99, 5, "pH 99pct")
check_null_print(tbl_pH_01, 5, "pH 1pct")

check_null_print(tbl_Temp_F_99, 5, "Temp 99pct")
check_null_print(tbl_Temp_F_01, 5, "Temp 1pct")

check_null_print(tbl_SpCond_uScm_99, 5, "SpCond 99pct")
check_null_print(tbl_SpCond_uScm_01, 5, "SpCond 1pct")

check_null_print(tbl_Turbidity_FNU_99, 5, "Turb 99pct")
check_null_print(tbl_Turbidity_FNU_01, 5, "Turb 1pct")

check_null_print(tbl_ChlA_EXO_ugL_99, 5, "ChlA 99pct")
check_null_print(tbl_ChlA_EXO_ugL_01, 5, "ChlA 1pct")

#++++ add remaining tables for each sonde parameter ++++
## JAP Note: ChlA_EXO should not return LNETN values, but it does ##

cat("\n\n")
```

```{r eval = lab_include, results = 'asis'}
cat("#### Lab Parameters {.tabset}", "\n\n")

check_null_print(tbl_ANC_ueqL_99, 5, "ANC 99pct")
check_null_print(tbl_ANC_ueqL_01, 5, "ANC 1pct")

check_null_print(tbl_TP_ugL_99, 5, "TP 99pct")
check_null_print(tbl_TP_ugL_01, 5, "TP 1pct")

check_null_print(tbl_TN_mgL_99, 5, "TN 99pct")
check_null_print(tbl_TN_mgL_01, 5, "TN 1pct")

check_null_print(tbl_DOC_mgL_99, 5, "DOC 99pct")
check_null_print(tbl_DOC_mgL_01, 5, "DOC 1pct")

check_null_print(tbl_ChlA_ugL_99, 5, "ChlA 99pct")
check_null_print(tbl_ChlA_ugL_01, 5, "ChlA 1pct")

#++++ add remaining tables for each lab parameter ++++

cat("\n\n")
```

```{r eval = lab_v_sonde_include, results = 'asis', fig.height = 6, fig.width = 7}
cat("#### Lab vs Sonde {.tabset}", "\n\n")

# Details code makes it a drop down
check_null_print(tbl_pH_10pct, 5, "pH diff")
cat("##### pH diff fig {.tabset}", "\n\n")
pctdiff_pH
cat("\n\n")

check_null_print(tbl_ChlA_EXO_ugL_10pct, 5, "ChlA diff")
cat("##### ChlA diff fig {.tabset}", "\n\n")
pctdiff_ChlA_EXO_ugL
cat("\n\n")
#++++ add remaining tables and figures for each sonde vs lab parameter ++++

cat("\n\n")
```

```{r eval = qc_include, results = "asis"}
cat("### Quality Control {.tabset}", "\n\n")
```

```{r eval = do899_include, results = 'asis'}
check_null_print(do_kbl, 4, "DOSat")

cat("\n\n")
```

```{r eval = qcsamp_include, results = 'asis', fig.height = 6, fig.width = 7}
cat("#### QC Samples {.tabset}", "\n\n")

check_null_print(tbl_pH_Lab_10pct_rep, 5, "pH diff")
cat("##### pH diff fig {.tabset}", "\n\n")
pctdiff_pH_Lab_rep
cat("\n\n")

check_null_print(tbl_ChlA_ugL_10pct_rep, 5, "ChlA diff")
cat("##### ChlA diff fig {.tabset}", "\n\n")
pctdiff_ChlA_ugL_rep
cat("\n\n")
```


```{r blanks, eval = blank_include, results = 'asis'}
cat("#### Blank Samples {.tabset}", "\n\n")

check_null_print(blank_kbl, 5, "TN TP")
cat("\n\n")

check_null_print(blank_kbl2, 5, "pH")
cat("\n\n")

check_null_print(blank_kbl3, 5, "ChlA")
cat("\n\n")
```

```{r eval = wquant_include, results = "asis"}
cat("### Water Quantity {.tabset}", "\n\n")
```

```{r eval = secchi_include, results = 'asis'}
cat("#### Secchi Depth {.tabset}", "\n\n")
check_null_print(tbl_SDepth_m_99, 5, "SDepth 99pct")
check_null_print(tbl_SDepth_m_01, 5, "SDepth 01pct")

cat("\n\n")
```

```{r eval = lakelev_include, results = 'asis'}
cat("#### Lake Level {.tabset}", "\n\n")
check_null_print(tbl_WaterLevel_m_99, 5, "WLevel 99pct")
check_null_print(tbl_WaterLevel_m_01, 5, "WLevel 01pct")
cat("\n\n")
```


```{r eval = disch_include, results = 'asis'}
cat("#### Discharge {.tabset}", "\n\n")
check_null_print(tbl_Discharge_cfs_99, 5, "Disch. 99pct")
check_null_print(tbl_Discharge_cfs_01, 5, "Disch. 01pct")
check_null_print(tbl_disch_0, 5, "Disch. NAs")
cat("\n\n")
```

```{r stage, eval = stage_include, results = 'asis'}
cat("#### Stage {.tabset}", "\n\n")
check_null_print(tbl_stage_0, 5, "Stage NAs")
cat("\n\n")

```
